Plots and tables summarizing results of Poisson simulations

### 2018-12-20 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

```{r knitr-opts, include=FALSE}
knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center")
```

@@

```{r table-row-and-col-names}
table.row.names <- c("SMASH","BMSM","Haar-Fisz")
table.col.names <- c("intensity (0.01,3)","intensity (1/8,8)",
                     "intensity (1/128,128)")
```

@@

This is the function used to simulate the "Spikes" data sets:

```{r spikes-function, fig.height=5, fig.width=10}
mu.s <- spike.f(t)
plot(t,mu.s,xlab = "",ylab = "",type = "l",
     main = "Spikes intensity function")
```

Summarize the results from the Spikes simulations in a table.

Comparison of methods for denoising Poisson data for the "Spikes"
test function for 3 different (min,max) intensities ((0.01,3),
(1/8,8), (1/128,128)). Performance is measured using MISE over 100
independent datasets, with smaller values indicating better
performance. Values colored in red indicates the smallest MISE amongst
all methods for a given (min, max) intensity.

```{r spikes-table, results="asis"}
mise.s.table   <- cbind(mise.s.1[methods],
                        mise.s.8[methods],
                        mise.s.128[methods])
rownames(mise.s.table) <- table.row.names
colnames(mise.s.table) <- table.col.names
print(xtable(mise.s.table),type = "html")
```

Summarize the results from the Spikes simulations in combined violin
and boxplots.

```{r spikes-violin-plots, fig.height=5, fig.width=7}
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
					                 mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
n     <- length(mise.ash.s.1)
pdat1 <- data.frame(method = rep(c("SMASH","BMSM","HF"),each = n),
 				    mise   = c(mise.ash.s.1,mise.BMSM.s.1,mise.hf.ti.r.s.1))
p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
      coord_flip()
      labs(x = "",y = "MISE") +
     theme(axis.line = element_blank(),
           axis.ticks.y = element_blank())
```

@@

### Angles data

```{r, results="asis"}
print(xtable(mise.ang.table,caption="Comparison of methods for denoising Poisson data for the ``Angles'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)). Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_ang",digits=2),type = "html")
```

### Heavisine data

@@

### Bursts data

@@

### Clipped Blocks data

@@

### Bumps data

>>>>

```{r knitr-opts, include=FALSE}
knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center",
                      results = "hold")
```

@@

```{r table-row-and-col-names}
table.row.names <- c("SMASH","BMSM","Haar-Fisz")
table.col.names <- c("(1/100,3)","(1/8,8)","(1/128,128)")
```

@@

This is the function used to simulate the "Spikes" data sets at
different ranges of intensities:

```{r plot-spikes-function, fig.height=4, fig.width=8}
mu.s <- spike.f(t)
plot(t,mu.s,xlab = "",ylab = "",type = "l")
```

This table summarizes the results from the Spikes simulations:

```{r spikes-table, results="asis"}
mise.s.table   <- cbind(mise.s.1[methods],
                        mise.s.8[methods],
                        mise.s.128[methods])
rownames(mise.s.table) <- table.row.names
colnames(mise.s.table) <- table.col.names
print(xtable(mise.s.table,caption = " "),type = "html",
      html.table.attributes = "border=0")
```

Each column shows results at a different range of intensities.  The
individual table entries give the average error (MISE) in the
estimates, in which the average is taken over the 100 data sets
simulated at the given range of intensities.

The combined violin-boxplots provide a visualization of the same
results:

```{r spikes-violin-plots, fig.height=3.5, fig.width=10}
m                  <- length(mise.ash.s.1)
method.labels      <- c("Haar-Fisz","BMSM","SMASH")
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
pdat1 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.1,mise.BMSM.s.1,mise.ash.s.1))
pdat8 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.8,mise.BMSM.s.8,mise.ash.s.8))
pdat128 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.s.128,mise.BMSM.s.128,mise.ash.s.128))
p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
      coord_flip() +
      labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
	  theme(axis.line = element_blank())
p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
	  scale_x_discrete(breaks = NULL) +
      coord_flip() +
      labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
	  theme(axis.line = element_blank())
p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
	  scale_x_discrete(breaks = NULL) +
      coord_flip() +
      labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
	  theme(axis.line = element_blank())
plot_grid(p1,p8,p128,nrow = 1,ncol = 3)
```

@@

Angles data
-----------

This is the function used to simulate the "Angles" data sets at
different ranges of intensities:

```{r plot-angles-function, fig.height=4, fig.width=8}
mu.ang <- dop.f(t)
sig <- ((2 * t + 0.5) * (t <= 0.15)) +
  ((-12 * (t - 0.15) + 0.8) * (t > 0.15 & t <= 0.2)) +
  0.2 * (t > 0.2 & t <= 0.5) + 
  ((6 * (t - 0.5) + 0.2) * (t > 0.5 & t <= 0.6)) +
  ((-10 * (t - 0.6) + 0.8) * (t > 0.6 & t <= 0.65)) +
  ((-0.5 * (t - 0.65) + 0.3) * (t > 0.65 & t <= 0.85)) +
  ((2 * (t - 0.85) + 0.2) * (t > 0.85))
mu.ang <- 3/5 * ((5/(max(sig) - min(sig))) * sig - 1.6) - 0.0419569
plot(t,mu.ang,xlab = "",ylab = "",type = "l")
```

This table summarizes the results from the Angles simulations:

```{r angles-table, results="asis"}
mise.ang.table   <- cbind(mise.ang.1[methods],
                          mise.ang.8[methods],
                          mise.ang.128[methods])
rownames(mise.ang.table) <- table.row.names
colnames(mise.ang.table) <- table.col.names
print(xtable(mise.ang.table,caption = " "),type = "html",
      html.table.attributes = "border=0")
```

Each column shows results at a different range of intensities.  The
individual table entries give the average error (MISE) in the
estimates, in which the average is taken over the 100 data sets
simulated at the given range of intensities.

The combined violin-boxplots provide a visualization of the same
results:

```{r angles-violin-plots, fig.height=3.5, fig.width=10}
mise.hf.ti.r.ang.1   <- colMeans(rbind(mise.hf.ti.r.4.ang.1,
                                       mise.hf.ti.r.5.ang.1,
                                       mise.hf.ti.r.6.ang.1,
					  				   mise.hf.ti.r.7.ang.1))
mise.hf.ti.r.ang.8   <- colMeans(rbind(mise.hf.ti.r.4.ang.8,
 									   mise.hf.ti.r.5.ang.8,
                                       mise.hf.ti.r.6.ang.8,
                                       mise.hf.ti.r.7.ang.8))
mise.hf.ti.r.ang.128 <- colMeans(rbind(mise.hf.ti.r.4.ang.128,
                                       mise.hf.ti.r.5.ang.128,
                                       mise.hf.ti.r.6.ang.128,
									   mise.hf.ti.r.7.ang.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.ang.1,mise.BMSM.ang.1,mise.ash.ang.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.ang.8,mise.BMSM.ang.8,mise.ash.ang.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.ang.128,mise.BMSM.ang.128,mise.ash.ang.128))
p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
      coord_flip() +
      labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
	  theme(axis.line = element_blank())
p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
	  scale_x_discrete(breaks = NULL) +
      coord_flip() +
      labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
	  theme(axis.line = element_blank())
p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
      geom_violin(fill = "skyblue",color = "skyblue") +
      geom_boxplot(width = 0.15,outlier.shape = NA) +
	  scale_x_discrete(breaks = NULL) +
      coord_flip() +
      labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
	  theme(axis.line = element_blank())
plot_grid(p1,p8,p128,nrow = 1,ncol = 3)
```

Heavisine data
--------------

This is the function used to simulate the "Heavisine" data sets at
different ranges of intensities:

```{r plot-heavisine-function, fig.height=4, fig.width=8}
heavi <- 4 * sin(4 * pi * t) - sign(t - 0.3) - sign(0.72 - t)
mu.hs <- heavi/sqrt(var(heavi)) * 1 * 2.99/3.366185
mu.hs <- mu.hs - min(mu.hs)
plot(t,mu.hs,xlab = "",ylab = "",type = "l")
```

@@

Bursts data
-----------

This is the function used to simulate the "Bursts" data sets at
different ranges of intensities:

```{r plot-bursts-function, fig.height=4, fig.width=8}
I_1 <- exp(-(abs(t - 0.2)/0.01)^1.2) * (t <= 0.2) +
       exp(-(abs(t - 0.2)/0.03)^1.2) * (t > 0.2)
I_2 <- exp(-(abs(t - 0.3)/0.01)^1.2) * (t <= 0.3) +
       exp(-(abs(t - 0.3)/0.03)^1.2) * (t > 0.3)
I_3 <- exp(-(abs(t - 0.4)/0.01)^1.2) * (t <= 0.4) +
       exp(-(abs(t - 0.4)/0.03)^1.2) * (t > 0.4)
mu.bur <- 2.99/4.51804 * (4 * I_1 + 3 * I_2 + 4.5 * I_3)
plot(t,mu.bur,xlab = "",ylab = "",type = "l")
```

@@

Clipped Blocks data
-------------------

This is the function used to simulate the "Clipped Blocks" data sets at
different ranges of intensities:

```{r plot-cb-function, fig.height=4, fig.width=8}
pos   <- c(0.1,0.13,0.15,0.23,0.25,0.4,0.44,0.65,0.76,0.78,0.81)
hgt   <- 2.88/5 * c(4,-5,3,-4,5,-4.2,2.1,4.3,-3.1,2.1,-4.2)
mu.cb <- rep(0,n)
for (j in 1:length(pos))
  mu.cb <- mu.cb + (1 + sign(t - pos[j])) * (hgt[j]/2)
mu.cb[mu.cb < 0] <- 0
plot(t,mu.cb,xlab = "",ylab = "",type = "l")
```

@@

Bumps data
----------

This is the function used to simulate the "Bumps" data sets at
different ranges of intensities:

```{r plot-bumps-function, fig.height=4, fig.width=8}
pos  <- c(0.1,0.13,0.15,0.23,0.25,0.4,0.44,0.65,0.76,0.78,0.81)
hgt  <- 2.97/5 * c(4,5,3,4,5,4.2,2.1,4.3,3.1,5.1,4.2)
wth  <- c(0.005,0.005,0.006,0.01,0.01,0.03,0.01,0.01,0.005,0.008,0.005)
mu.b <- rep(0, n)
for (j in 1:length(pos))
  mu.b <- mu.b + hgt[j]/((1 + (abs(t - pos[j])/wth[j]))^4)
plot(t,mu.b,xlab = "",ylab = "",type = "l")
```
